Growth model analysis 3spp WB

### 2018-07-31 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
add relImp graph

```{r Load data, message=FALSE}
library(arm)
library(linkedModels)
library(arrayhelpers)
library(tidyverse)
library(gridExtra)

@@

stats3Spp <- anov <- list()

for( speciesForProj in c('bkt','bnt','ats') ){

@@

    sizeStats1 <- summarizeLens(sizeMat,testRow)
    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
  }
  endTime <- Sys.time()
  (elapsed <- endTime - startTime)

@@

  anov[[speciesForProj]] <- anova( lm( lenMean ~ temp + flow + bkt + bnt + ats, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult))) )

@@

ggplot(sizeStats, aes())

matplot(t(sizeMat[2,,]))

ggplot(predLen %>% filter(iter %in% 1:10), aes(occ,len, group=ind)) +
  geom_point(aes(color=ind))+
  geom_line(aes(color=ind)) +
  theme(legend.position = 'none')+
  facet_wrap(~iter)

>>>>

```{r Load data, message=FALSE}
library(arm)
library(relaimpo)
library(linkedModels)
library(arrayhelpers)
library(tidyverse)
library(gridExtra)

@@

stats3Spp <- anov <- elapsed <- lm <- relImp <- list()
spp <- c('bkt','bnt','ats')

for( speciesForProj in spp ){

@@

    sizeStats1 <- summarizeLens(sizeMat,testRow)
    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
  }
  endTime <- Sys.time()
  (elapsed[[speciesForProj]] <- endTime - startTime)

@@

  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt^2, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult)))

  relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)

  anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )

@@

# make bar chart of relative importance of each variable for each spp
rI <- cbind(data.frame(bktRI = relImp[['bkt']]$lmg), data.frame(bntRI = relImp[['bnt']]$lmg), data.frame(atsRI = relImp[['ats']]$lmg)) %>%
        rownames_to_column() %>% gather(key=rowname) %>% mutate(var = rep(1:length(relImp[['bkt']]$lmg),length(spp)))

ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
  geom_col(position='dodge') +
  scale_x_discrete('Parameter name',
                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow')) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme( legend.position = 'none')

ggsave('figures/3Spp_WB/relImp.png', width = 9, height = 7, units='in')
